Ion pairing controls rheological properties of polyelectrolyte crocodile line hydrogels

### 2016-01-22 ion_pairing_paper.tex
Cyrille citations of DSC and water sorbtion

In the case polyelectrolytes with fluoride and chloride counterion, we observe no exo or endothermic transition below \SI{200}{\celsius}. By contrast, we observe a broad endothermic peak when iodide and bromide are used as counterions. Quite remarkably,we found a similar peak temperature (84-\SI{85}{\celsius}) for \ce{PIm+I-} and \ce{PPyr+I-}, see Figure~\ref{fig:dsc}. When bromide counterions are present, we observe a significant increase of the peak temperature (114-\SI{115}{\celsius}) but again, with a similar value between \ce{PIm+Br-} and \ce{PPyr+Br-} as shown in Figure~\ref{fig:dsc}. The overall shape and position of the DSC peaks is very reminiscent of previously reported data for various naturally occuring or synthetic poly(electrolytes).[ Li, L.; Hsieh, Y.-L., Ultra-fine polyelectrolyte fibers from electrospinning of poly(acrylic acid). Polymer 2005, 46 (14), 5133-5139. ; Ostrowska-Czubenko, J.; Gierszewska-Drużyńska, M., Effect of ionic crosslinking on the water state in hydrogel chitosan membranes. Carbohydrate Polymers 2009, 77 (3), 590-598., Deb, T. K.; Ramireddy, B.; Moin, A.; Shivakumar, H. G., In vitro-in vivo evaluation of xanthan gum and eudragit inter polyelectrolyte complex based sustained release tablets. International Journal of Pharmaceutical Investigation 2015, 5 (1), 65-72.), Sarmento, B.; Ferreira, D.; Veiga, F.; Ribeiro, A., Characterization of insulin-loaded alginate nanoparticles produced by ionotropic pre-gelation through DSC and FTIR studies. Carbohydrate Polymers 2006, 66 (1), 1-7.) It is generally attributed to desorption of weakly bound water from the polymer network. Its presence in the polymer samples where bromide and iodide are used as couterions suggests that adsorbed water could play a role in solvating the dissociated ion pairs in the latter; conversely, its absence for chloride and fluoride counterions suggests that dissociation is not effective because of stronger ion pair interaction.

>>>>

In the case polyelectrolytes with fluoride and chloride counterion, we observe no exo or endothermic transition below \SI{200}{\celsius}. By contrast, we observe a broad endothermic peak when iodide and bromide are used as counterions. Quite remarkably,we found a similar peak temperature (84-\SI{85}{\celsius}) for \ce{PIm+I-} and \ce{PPyr+I-}, see Figure~\ref{fig:dsc}. When bromide counterions are present, we observe a significant increase of the peak temperature (114-\SI{115}{\celsius}) but again, with a similar value between \ce{PIm+Br-} and \ce{PPyr+Br-} as shown in Figure~\ref{fig:dsc}. The overall shape and position of the DSC peaks is very reminiscent of previously reported data for various naturally occuring or synthetic poly(electrolytes)\cite{Li2005,Sarmento2006,Ostrowska-Czubenko2009a,Moin2015}. It is generally attributed to desorption of weakly bound water from the polymer network. Its presence in the polymer samples where bromide and iodide are used as couterions suggests that adsorbed water could play a role in solvating the dissociated ion pairs in the latter; conversely, its absence for chloride and fluoride counterions suggests that dissociation is not effective because of stronger ion pair interaction.
